|

### 2020-09-23 paper/paper.Rmd
done up to applications section

While the radial transformation can in general be used with any low-dimensional display that suffers from data piling, it is most useful when combined with a dynamic display showing a sequence of interpolated low-dimensional projections obtained when running a tour. We have implemented it as a new display method `display_sage` in the `tourr` package [@tourr] in R [@rref].

>>>>

While the radial transformation can in general be used with any low-dimensional display that suffers from data crowding, it is most useful when combined with a dynamic display showing a sequence of interpolated low-dimensional projections obtained when running a tour. We have implemented it as a new display method called `display_sage` in the `tourr` package [@tourr] in R [@rref].
